Enhancing the prediction of sales for newly published books by means of computational intelligence methods

### 2016-05-05 paper.tex
Changing a footnote into a reference as asked by @JJ :D

Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books\footnote{\url{https://en.wikipedia.org/wiki/List_of_Dewey_Decimal_classes}}, and the existing similarity relationship between the books inside a class or subclass. So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance. The same reasoning can be applied to subclasses.

>>>>

Therefore, in order to create simpler and more accurate prediction models, and with the aim to provide them as a useful decision-aid tool for the publisher, we have transformed the categorical variable \texttt{subject1} into a numerical one, considering it refers to a code of the Dewey Decimal Classification system for books \cite{wiki:dewey}, and the existing similarity relationship between the books inside a class or subclass. So, for instance, all the books inside subdivisions of class 200, `Religion', are considered as similar regarding their topics, so they could be also close in terms of distance. The same reasoning can be applied to subclasses.
